EEG2fMRI: Cross-Modal Synthesis for Functional Neuroimaging

### 2021-04-30 article/article.tex
Update

This state of affairs suggests that self-supervised approaches are more suitable candidates for attempting this mapping. Large amounts of uni-modal EEG data are available, and the same is true for uni-modal fMRI data, although to a less extent.

>>>>

This state of affairs suggests that self-supervised approaches might be more suitable candidates for attempting the EEG-fMRI mapping. Large amounts of uni-modal EEG data are available, and the same is true for uni-modal fMRI data, although to a lesser extent. Approaches which incorporate both types of uni-modal data might be more effective than ones which incorporate smaller multi-modal dataset. This resembles the shift towards unsupervised methods of machine translation where sufficiently large paired corpora do not exist.

Generating synthetic data based on an existing multi-modal dataset might be another way of tackling the issue of limited samples. While generative models have been successfully used to synthesize uni-modal data, the same cannot be said about synchronous multi-modal data. An even simpler solution to the problem might be to join all publicly available multi-modal EEG-fMRI datasets into one larger one, and learning the mapping based on the resulting dataset. However, those few datasets available which match the criterion typically use scanners with wildly different specifications. From the number of EEG channels used to the sampling frequency of the fMRI scanner, it might be challenging to merge those into a generic dataset.

Learning the mapping between simultaneous EEG and fMRI recordings remains an open challenge which might enable powerful tools for neuroscientists of various specializations. The limited quantity of data currently available appears to be a major obstacle in solving this task.
